---
title: "FP"
author: "Alice Mee Seon Chung"
date: "5/24/2018"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = FALSE,
                      cache = T)
library(tidyverse)
library(knitr)
library(broom)
library(stringr)
library(modelr)
library(forcats)
library(tidytext)
library(wordcloud)
library(scales)
library(rtweet)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(ggmap)
library(reshape2)
library(maps)
library(foreign)
library(readstata13)
library(stargazer)
library(lmtest)
library(coefplot)
<<<<<<< HEAD
library(tidyverse)
library(knitr)
library(broom)
library(stringr)
library(modelr)
library(forcats)
library(tidytext)
library(wordcloud)
library(scales)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(ggmap)
library(reshape2)
library(maps)
library(gtools)
library(plyr)
library(ggplot2)
library(dplyr)
library(plotly)
library(shiny)
library(flexdashboard)
packageVersion('plotly')
set.seed(1)
options(digits = 3)
set.seed(1234)
theme_set(theme_minimal())
setwd("~/Desktop/2018SPRING/DV/fp-nxu-achung/")

=======
library(gtools)

options(digits = 3)
set.seed(1234)
theme_set(theme_minimal())
```

```{r}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))
>>>>>>> 44665b6c6e3770df381710d0d69aac5fd8aa1253
df2010<-read.dta13('data/data_2010.dta',
                   missing.type = T,
                   nonint.factors = T,
                   generate.factors = T) %>%
  mutate_each(funs(replace(., . == "Not applicable", NA))) %>%
  mutate_each(funs(replace(., . == "Not applicable_(-8)", NA))) %>%
  mutate_each(funs(replace(., . == "Unknown", NA))) 

df2014<-read.dta13('data/data_2014.dta',
                   missing.type = T,
                   nonint.factors = T,
                   generate.factors = T) %>%
  mutate_each(funs(replace(., . == "Not applicable", NA))) %>%
  mutate_each(funs(replace(., . == "Not applicable_(-8)", NA))) %>%
  mutate_each(funs(replace(., . == "Unknown", NA)))
<<<<<<< HEAD
```
```{r, echo=FALSE}
joined <- df2010 %>%
  inner_join(df2014, by = "pid", suffix = c("_2010", "_2014"))

joined <- joined %>% 
  mutate(income_diff = income_2014 - income_2010)%>%
  mutate(provcd_2010=as.character(joined$provcd_2010),
         provcd_2014=as.character(joined$provcd_2014))%>%
  mutate(provcd_2010=replace(as.character(joined$provcd_2010), 
                     joined$provcd_2010 == "Guangxi Zhuang Autonomous Region",
                     "Guangxi"),
         provcd_2014=replace(as.character(joined$provcd_2014), 
                     joined$provcd_2014 == "Guangxi Zhuang Autonomous Region",
                     "Guangxi"),
          provcd_2014=replace(as.character(joined$provcd_2014), 
                     joined$provcd_2014 =="Xinjiang Uygur Autonomous Region",
                     "Xinjiang"))

joined1<-joined%>%
  filter(!is.na(joined$income_2014)&!is.na(joined$income_2010)
                &!is.na(joined$provcd_2010)&!is.na(joined$provcd_2014)
                &!is.na(joined$urban_2010)&!is.na(joined$urban_2014))%>%
  mutate(gender_10 = case_when(gender_2010 =="Male" ~ 1,
                        gender_2010 == "Female_(0)"  ~ 0,
                        gender_2010 =="Female_(5)" ~ 0,
                        TRUE ~ 5), gender_14=case_when(gender_2014 =="Male" ~ 1,
                        gender_2014 == "Female_(0)"  ~ 0,
                        gender_2014 =="Female_(5)" ~ 0,
                        TRUE ~ 5))%>%
  mutate(income_2010=as.numeric(income_2010), income_2014=as.numeric(income_2014),
         gender_2010=as.numeric(gender_2010), gender_2014=as.numeric(gender_2014))

joined_10_prov<-joined1%>%
  group_by(provcd_2010)%>%
  summarise(mean_income = mean(income_2010),
            m = sum(gender_10==1), f = sum(gender_10==0),
            r = sum(gender_10==1)/sum(gender_10==0),
            count=n(), year = 2010)%>%
  as.data.frame()

joined_14_prov<-joined1%>%
  group_by(provcd_2014)%>%
  summarise(mean_income = mean(income_2014), 
            m = sum(gender_14==1), f = sum(gender_14==0),
            r = sum(gender_14==1)/sum(gender_14==0),
            count=n(), year = 2014)%>%
  as.data.frame()
colnames(joined_10_prov)[1]<-'provcd'
colnames(joined_14_prov)[1]<-'provcd'
merged<-left_join(joined_10_prov, joined_14_prov, by='provcd')
merged$diffincome<-merged$mean_income.y-merged$mean_income.x

joined_10_rural<-joined1%>%
  group_by(provcd_2010, urban_2010)%>%
  summarise(mean_income = mean(income_2010), 
            m = sum(gender_10==1), f = sum(gender_10==0),
            r = sum(gender_10==1)/sum(gender_10==0),
            count=n(), year = 2010)%>%
  as.data.frame()

joined_14_rural<-joined1%>%
  group_by(provcd_2014, urban_2014)%>%
  summarise(mean_income = mean(income_2014), 
            m = sum(gender_14==1), f = sum(gender_14==0),
            r = sum(gender_14==1)/sum(gender_14==0),
            count=n(), year = 2014)%>%
  as.data.frame()
colnames(joined_10_rural)[1]<-'provcd'
colnames(joined_14_rural)[1]<-'provcd'
colnames(joined_10_rural)[2]<-'urban'
colnames(joined_14_rural)[2]<-'urban'
merged_rural<-inner_join(joined_10_rural, joined_14_rural, by=c('provcd','urban'))
merged_rural$diffincome<-merged_rural$mean_income.y-merged_rural$mean_income.x
```

Input {.sidebar}
---------------------------------------------------
```{r, echo=FALSE}
selectizeInput('type', label = "Select Catetory",
            choices = c("By Province","By Rural/Urban"), selected = "By Province")
#selectizeInput('year', label = "Select Year",
#            choices = unique(mer$year), selected = 2010)
selectizeInput('province', label = "Select Province",
            choices = c("All", sort(as.character(unique(merged$provcd)))),
            selected = "All")
```
```{r, include=FALSE, eval=FALSE}
ggplot(data = merged, aes(x = diffincome, y = r.y, 
               fill = provcd))+ 
  geom_point(aes(size = count.y), shape = 21, alpha = 0.7)+
  labs(size = 'Province ID')+
  geom_hline(yintercept = 1, color = "blue", linetype = 2, size = 0.5) +
  scale_size_continuous(range = c(1,8.5)) +
  scale_x_continuous(name = "Difference between Mean of Incomes of 2014 and 2010")+#, limits = c(0, 40000)) +
  scale_y_continuous(name = "Gender Ratio (Male/Female)(%)")+#, limits = c(0.8, 1.2)) +
  guides(fill=guide_legend(title='Province ID'))+
  theme(legend.position = "bottom", 
        panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, echo=FALSE}
plot_province<-function(data){
  ggplot(data = data,
             aes(x = diffincome, y = r.y, 
               fill = provcd))+ 
  geom_point(aes(size = count.y), shape = 21, alpha = 0.7)+
  labs(size = 'Province ID')+
  geom_hline(yintercept = 1, color = "blue", linetype = 2, size = 0.5) +
  scale_size_continuous(range = c(1,8.5)) +
  scale_x_continuous(name = "Difference between Mean of Incomes of 2014 and 2010",
                     limits = c(-300,-20)) +
  scale_y_continuous(name = "Gender Ratio (Male/Female)(%)", limits = c(0.5, 2)) +
  guides(fill=guide_legend(title='Province ID'))+
  theme(legend.position = "bottom", 
        panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())}

plot_province_city<- function(data){
  ggplot(data =data,
             aes(x = diffincome, y = r.y, 
               fill = provcd))+ 
  geom_point(aes(size = count.y), shape = 21, alpha = 0)+
  geom_point(data = filter(data, 
                           provcd %in% input$province), 
             aes(size = count.x, fill='blank'), shape = 21) +
  labs(size = 'Province ID')+
  geom_hline(yintercept = 1, color = "blue", linetype = 2, size = 0.5) +
  scale_size_continuous(range = c(1,8.5)) +
  scale_x_continuous(name = "Difference between Mean of Incomes of 2014 and 2010",
                     limits = c(-300, -20)) +
  scale_y_continuous(name = "Gender Ratio (Male/Female)(%)", limits = c(0.5, 2)) +
  guides(fill=guide_legend(title='Province ID'))+
  theme(legend.position = "bottom", 
        panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())}


plot_urban<-function(data) {
  ggplot(data = data,
             aes(x = diffincome, y = r.y,
                 fill = urban, label = provcd))+
  geom_point(aes(size = count.y), shape = 21, alpha = 0.7)+
  labs(size = 'Rural/Urban')+
  geom_hline(yintercept = 1, color = "blue", linetype = 2, size = 0.5) +
  scale_size_continuous(range = c(1,8.5)) +
  scale_x_continuous(name = "Difference between Mean of Incomes of 2014 and 2010",
                     limits = c(-300, -20)) +
  scale_y_continuous(name = "Gender Ratio (Male/Female)(%)", limits = c(0.5, 2)) +
  theme(panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())+
  scale_fill_manual(values=c("#1EBA28","#F1A1D5"))}


plot_urban_city<- function(data){
  ggplot(data = data,
             aes(x = diffincome, y = r.y, 
               fill = urban, label = provcd))+ 
  geom_point(aes(size = count.y), shape = 21, alpha = 0)+
  geom_point(data = filter(data, 
                           provcd %in% input$province), 
             aes(size = count.y, fill=urban), shape = 21) +
  labs(size = 'Rural/Urban')+
  geom_hline(yintercept = 1, color = "blue", linetype = 2, size = 0.5) +
  scale_size_continuous(range = c(1,8.5)) +
  scale_x_continuous(name = "Difference between Mean of Incomes of 2014 and 2010",
                     limits = c(-300, -20)) +
  scale_y_continuous(name = "Gender Ratio (Male/Female)(%)", limits = c(0.5, 2)) +
  guides(fill=guide_legend(title='Province ID'))+
  theme(legend.position = "bottom", 
        panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())+
  scale_fill_manual(values=c("#1EBA28","#F1A1D5","black"))}
```

Row {data-width=800}
--------------------------------------------------

```{r 1, echo=FALSE}
renderPlotly(
  if (input$type == 'By Province'){
    if(input$province=='All') {
  pp<-plot_province(merged)}
    else{
      pp<-plot_province_city(merged)
    }
  }
else{
  if(input$province=='All') {
  pp1<-plot_urban(merged_rural)}
    else{
      pp1<-plot_urban_city(merged_rural)
}})
```


```{r, eval=FALSE, include=FALSE}
lm1<-lm(income~.-pid-fid-cid-provcd-countyid-hukou-inc_lastyr-stage_educ
        ,data=df2010)

summary(lm1)

lm2<-lm(income~.-pid-fid-fid12-fid10-cid-provcd-countyid-stage_educ-te4
        ,data=df2014)

summary(lm2)
stargazer(ss$coefficients, type = 'text')
coefplot(lm1)
coefplot(lm2)

```


=======


# dat <- smartbind(df2010, df2014)

dat <- df2010 %>%
  inner_join(df2014, by = "pid", suffix = c("_2010", "_2014"))
```


```{r}
joined <- dat %>% 
  mutate(income_2014 = as.numeric(income_2014),
         income_2010 = as.numeric(income_2010),
         income_diff = income_2014 - income_2010) %>%
  mutate(
    convenience_diff = as.numeric(ca301_a_1_2014) - as.numeric(ca301_a_1_2010),
    kindergarten_diff = as.numeric(ca301_a_2_2014) - as.numeric(ca301_a_2_2010),
    primsch_diff = as.numeric(ca301_a_3_2014) - as.numeric(ca301_a_3_2010),
    hospital_diff = as.numeric(ca301_a_4_2014) - as.numeric(ca301_a_4_2010),
    drugstore_diff = as.numeric(ca301_a_5_2014) - as.numeric(ca301_a_5_2010),
    temple_diff = as.numeric(ca301_a_6_2014) - as.numeric(ca301_a_6_2010),
    ancestral_diff = as.numeric(ca301_a_7_2014) - as.numeric(ca301_a_7_2010),
    church_diff = as.numeric(ca301_a_8_2014) - as.numeric(ca301_a_8_2010),
    actvty_diff = as.numeric(ca301_a_9_2014) - as.numeric(ca301_a_9_2010),
    nursing_diff = as.numeric(ca301_a_10_2014) - as.numeric(ca301_a_10_2010),
    physfacty_diff = as.numeric(ca301_a_11_2014) - as.numeric(ca301_a_11_2010),
    playgrd_diff = as.numeric(ca301_a_12_2014) - as.numeric(ca301_a_12_2010),
    letterbox_diff = as.numeric(ca301_a_14_2014) - as.numeric(ca301_a_14_2010),
    comm_website = as.numeric(ca301_a_15_2014) - as.numeric(ca301_a_15_2010),
    areasize_2010 = as.numeric(ca4r_2010),
    areasize_2014 = as.numeric(ca4r_2014),
    watersource_change = ifelse(ca5_2014 == ca5_2010, 1, 0),
    cooking_change = ifelse(ca6_2014 == ca6_2010, 1, 0),
    pop_change = as.numeric(cb2_2014) - as.numeric(cb2_2010),
    elec_access_change = 1,
    cableradio_access_change = 1,
    cabletv_access_change = 1,
    postal_access_change = 1,
    tele_access_change = 1,
    cell_access_change = 1,
    road_access_change = 1,
    rail_access_change = 1,
    tap_access_change = 1,
    gas_access_change = 1,
    localenterprise_access_change = 1,
    commelect_access_change = 1,
    transit_access_change = 1,
    bus_access_change = 1,
    subway_access_change = 1,
    
    elec_access_2014 = 1,
    cableradio_access_2014 = 1,
    cabletv_access_2014 = 1,
    postal_access_2014 = 1,
    tele_access_2014 = 1,
    cell_access_2014 = 1,
    road_access_2014 = 1,
    rail_access_2014 = 1,
    tap_access_2014 = 1,
    gas_access_2014 = 1,
    localenterprise_access_2014 = 1,
    commelect_access_2014 = 1,
    transit_access_2014 = 1,
    bus_access_2014 = 1,
    subway_access_2014 = 1,
    elec_access_2010 = ifelse(as.numeric(ca301_a_1_change)<2010 & as.numeric(ca301_a_1_change) >0, 1, 0),
    cableradio_access_2010 = ifelse(as.numeric(ca301_a_2_change)<2010 & as.numeric(ca301_a_2_change) >0, 1, 0),
    cabletv_access_2010 = ifelse(as.numeric(ca301_a_3_change)<2010 & as.numeric(ca301_a_3_change) >0, 1, 0),
    postal_access_2010 = ifelse(as.numeric(ca301_a_4_change)<2010 & as.numeric(ca301_a_4_change) >0, 1, 0),
    tele_access_2010 = ifelse(as.numeric(ca301_a_5_change)<2010 & as.numeric(ca301_a_5_change) >0, 1, 0),
    cell_access_2010 = ifelse(as.numeric(ca301_a_6_change)<2010 & as.numeric(ca301_a_6_change) >0, 1, 0),
    road_access_2010 = ifelse(as.numeric(ca301_a_7_change)<2010 & as.numeric(ca301_a_7_change) >0, 1, 0),
    rail_access_2010 = ifelse(as.numeric(ca301_a_8_change)<2010 & as.numeric(ca301_a_8_change) >0, 1, 0),
    tap_access_2010 = ifelse(as.numeric(ca301_a_9_change)<2010 & as.numeric(ca301_a_9_change) >0, 1, 0),
    gas_access_2010 = ifelse(as.numeric(ca301_a_10_change)<2010 & as.numeric(ca301_a_10_change) >0, 1, 0),
    localenterprise_access_2010 = ifelse(as.numeric(ca301_a_11_change)<2010 & as.numeric(ca301_a_11_change) >0, 1, 0),
    commelect_access_2010 = ifelse(as.numeric(ca301_a_12_change)<2010 & as.numeric(ca301_a_12_change) >0, 1, 0),
    transit_access_2010 = ifelse(as.numeric(ca301_a_13_change)<2010 & as.numeric(ca301_a_13_change) >0, 1, 0),
    bus_access_2010 = ifelse(as.numeric(ca301_a_14_change)<2010 & as.numeric(ca301_a_14_change) >0, 1, 0),
    subway_access_2010 = ifelse(as.numeric(ca301_a_15_change)<2010 & as.numeric(ca301_a_15_change) >0, 1, 0),
    dist_committe_nearesttown_change = as.numeric(cg1_2014) - as.numeric(cg1_2010),
    dist_committe_countycap_change = as.numeric(cg2_2014) - as.numeric(cg2_2010),
    dist_committe_provcap_change = as.numeric(cg3_2014) - as.numeric(cg3_2010),
    whether_mine_change = as.numeric(cg4_2014) - as.numeric(cg4_2010),
    agri_gdp_change = as.numeric(ch3_2014) - as.numeric(ch3_2010),
    nonagri_gdp_change = as.numeric(ch4_2014) - as.numeric(ch4_2010),
    income_percap_change = as.numeric(ch5_2014) - as.numeric(ch5_2010))
  
joined <- joined[!is.na(joined$income_diff) & !is.na(joined$provcd_2014) & !is.na(joined$urban_2014), ]
lm <- income_diff ~  
```















>>>>>>> 44665b6c6e3770df381710d0d69aac5fd8aa1253
